---
title: "Life Expectancy - Human Development Index (HDI)"
author: "Juanma Martinez"
date: "12 August 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Set working directory


### Packages to upload

library(dplyr)
library(plotly)
library(tidyr)
library(scales)
library(readr)

####################################################################
#############   Upload the files and join the tables   #############
####################################################################


#############   Upload the file: HDI:  First Document

Human_development_index <- read_csv("Human development index.csv")
View(Human_development_index)

## gather

Human_Development_Index_HDI<-gather(Human_development_index, Year, HDI, 2:27)
View(Human_Development_Index_HDI)


#############  Upload the file: Continent and country: Second Document


Continent_Country <- read_csv("Continent_Country.csv")
View(Continent_Country)

## name
names(Continent_Country)[1]<- "Country"
names(Continent_Country)[2]<- "Continent"


#############  join

Human_Development_Index_HDI_join<- Human_Development_Index_HDI%>% inner_join(Continent_Country, by= "Country")

View(Human_Development_Index_HDI_join)


#############   Upload the file: Life Expectacnty: Third Document


LifeExpectancy <- read_csv("LifeExpectancy.csv")
View(LifeExpectancy)

## name

names(LifeExpectancy)[1]<-"Country"

## gather

LifeExpectancy_gather<- gather(LifeExpectancy, year, Life_Expectancy, '1990':'2015')%>% select(1,"year","Life_Expectancy")

View(LifeExpectancy_gather)

names(LifeExpectancy_gather)[2]<-"Year"


#############   Join

Human_Development_Index_HDI_join_LE<- Human_Development_Index_HDI_join%>% inner_join(LifeExpectancy_gather, by= c("Country","Year"))

View(Human_Development_Index_HDI_join_LE)


#############  Upload the file: Population: Fourth Document

Population <- read_csv("Population.csv")
View(Population)

## gather

Population<-gather (Population, Year, Population, `1990`:`2015`)%>% select(1, "Year", "Population")

View(Population)


#############   Join

Human_Development_Index_HDI_join_LE_POP<- Human_Development_Index_HDI_join_LE%>%inner_join(Population, by=c("Country", "Year")) 


View(Human_Development_Index_HDI_join_LE_POP)

data<-Human_Development_Index_HDI_join_LE_POP


####################################################################
#############   Prepare the data for plotly            #############
####################################################################


#############   reorder

data <-data[c(1,4,2,3,5,6)]

View(data)


#############   omit na rows

data_plotly<-na.omit(data)  

View(data_plotly)

#############   Round Life Expectancy to two number

data_plotly$Life_Expectancy<-round(data_plotly$Life_Expectancy, 2)

View(data_plotly)


#############   Create csv file

write.csv(data_plotly, file="data_plotly.csv", row.names = FALSE)

colnames(data_plotly)


```

## Life Expectancy - Human Development Data

This document provides an analysis of Life Expectancy and Human Development Data by country.

Data sources used:

- [World bank](https://data.worldbank.org/) for Life expectancy

- [HDI information](http://hdr.undp.org/en/content/human-development-index-hdi) for HDI data and definition.


```{r echo=FALSE, results='asis', warning = FALSE}
library(knitr)
library(kableExtra)

kable(data_plotly[1:5,], "html", caption = "Sample Data Table.", align=c(rep('c', 5))) %>%  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")

```

## Plotly


For the analysis and plotly visualization, We have used **three different variables**. 

1. **Life Expectancy**   (y axis)

2. **Human Development Index (HDI)**  (x axis)

3. **Population** (bubble size)





-  **Colour and Bubble Size**


Colour refers to continent and bubble size is according to Population size. 




-  **Animation**


Below the graph, we have a "play" button which can be used to play the animated plotly and see the yearly trend.

When we hover over one bubble point, we can see all the information on that specific country.



-  **Legend - Filter**


We can use the legend in the right-hand-side to filter countries within a specific continent. 

By default, the graph will show all countries in all continents. 

If we click one continent, the font letter from that continent will turn grey which means that all countries within that continent will not display on the graph.

If we double-click one continent, we will only see the countries within that continent.

This is very useful in order to compare yearly trend among different countries.

```{r pressure, echo=FALSE, warning = FALSE}
####################################################################
#############   Prepare the data for plotly            #############
####################################################################

p <-   plot_ly(data_plotly, 
               x = ~HDI, 
               y = ~Life_Expectancy, 
               color = ~Continent, 
               frame = ~Year, 
               size = ~Population,
               text =  ~paste('</br> Country: ', Country,
                              '</br> Year: ', Year,
                              '</br> Population: ', comma_format()(Population),
                              '</br> HDI: ', HDI,
                              '</br> Life Expectancy (years): ', round(Life_Expectancy,2)), 
               
               
               hoverinfo = "text",
               type = 'scatter',
               mode = 'markers'
) %>%
  layout(xaxis = list(range = c(0, 1), title = 'Human Development Index (HDI)'),
         yaxis = list(range = c(0, 100), title = 'Life Expectancy'),
         title = 'Life Expectancy -  HDI')

p
```

## Code, questions and feedback




The code for this article is publish in my [github account](https://github.com/JuanmaMN) in this [file](https://github.com/JuanmaMN/plotly/edit/master/Life%20Expectancy%20-%20HDI) 

Please feel free to reach out for any question or feedback.
