---
title: "Life Expectancy - HDI - 1990 - 2016"
author: "Juanma Martinez"
date: "5 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(plotly)
library(tidyr)
library(scales)
library(webshot)
library(readr)
library(knitr)
library(kableExtra)
library(readxl)



library(readr)
data_plotly <- read_csv("data_plotly.csv")
View(data_plotly)
```

## Life Expectancy - Human Development Data

This document provides an analysis of Life Expectancy and Human Development Data by country.

Data sources used:

- [World bank](https://data.worldbank.org/) for Life expectancy

- [HDI information](http://hdr.undp.org/en/content/human-development-index-hdi) for HDI data and definition.

```{r echo=FALSE, results='asis', warning = FALSE}


kable(data_plotly[1:5,], "html", caption = "Sample Data Table.", align=c(rep('c', 5))) %>%  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")
```

## Plotly


For the analysis and plotly visualization, We have used **three different variables**. 

1. **Life Expectancy**   (y axis)

2. **Human Development Index (HDI)**  (x axis)

3. **Population** (bubble size)





-  **Colour and Bubble Size**


Colour refers to country and bubble size is according to Population size. 




-  **Animation**


Below the graph, we have a "play" button which can be used to play the animated plotly and see the yearly trend.

When we hover over one bubble point, we can see all the information on that specific country.



-  **Legend - Filter**


We can use the legend in the right-hand-side to filter countries within a specific continent. 

By default, the graph will show all countries in all continents. 

If we click one continent, the font letter from that continent will turn grey which means that all countries within that continent will not display on the graph.

If we double-click one continent, we will only see the countries within that continent.

This is very useful in order to compare yearly trend among different countries.

```{r pressure, echo=FALSE, warning=FALSE}
p <-   plot_ly(data_plotly, 
               x = ~HDI, 
               y = ~Life_Expectancy, 
               color = ~Continent, 
               frame = ~Year, 
               size = ~Population,
               text =  ~paste('</br> Country: ', Country,
                              '</br> Year: ', Year,
                              '</br> Population: ', comma_format()(Population),
                              '</br> HDI: ', HDI,
                              '</br> Life Expectancy (years): ', round(Life_Expectancy,2)), 
               
               
               hoverinfo = "text",
               type = 'scatter',
               mode = 'markers'
) %>%
  layout(xaxis = list(range = c(0, 1), title = 'Human Development Index (HDI)'),
         yaxis = list(range = c(0, 100), title = 'Life Expectancy'),
         title = 'Life Expectancy -  HDI - 1990 - 2016')

p
```

## Code, questions and feedback




The code for this article is published in my [github account](https://github.com/JuanmaMN).

Please feel free to reach out for any question or feedback.