---
title: Climate at a Glance - Global Temperature Anomalies
author: Juanma
date: '2020-09-03'
slug: climate-at-a-glance-global-temperature-anomalies
categories:
  - R
tags:
  - R
  - World Data
image:
  caption: 'Photo by Jacqueline Godany on Unsplash'
  focal_point: ''
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(ggplot2)
library(plotly)

library(readxl)
Temperature <- read_excel("data - Temperature.xlsx")
View(Temperature)


Temperature$colour <- ifelse(Temperature$Value < 0, "firebrick1","steelblue")

Temperature_2<-select(Temperature,1:2)
```


<br>

<h2 style="text-align: center;">Global Land and Ocean Temperature Anomaly data - Time Series </h2>

<br>



[The National Oceanic and Atmospheric Administration](https://www.noaa.gov/) has published the time series of temperature anomalies.

Average temperature data shows a rise in global average temperature over the past several decades. 

- [Data source](https://www.ncdc.noaa.gov/cag/global/time-series)

- [For more information](https://www.ncdc.noaa.gov/cag/global/data-info)

Please find the analysis using both plotly and ggplot as a project.


<br>

<h2 style="text-align: center;">Global Land and Ocean Temperature Anomalies </h2>

<br>

```{r plot, echo=FALSE, warning = FALSE}


 plot_ly(Temperature, 
         x=~Year, 
         y=~Value, 
         mode="markers", 
         #hoverinfo = "text",
         type="bar", 
         color=~colour , 
         text = ~paste('Year: ', Year, '</br> Value(°C): ', Value)) %>% 
   layout(xaxis = list(title = ""), yaxis = list(title = "anomaly(°C)"),
         font = list(
           family = "Arial",
           size = 10)
          )%>% 
  hide_legend()%>% 
  layout(plot_bgcolor='#f4efe1', autosize = F) %>% 
  layout(paper_bgcolor='#f4efe1')  %>%
  add_annotations(xref = 'paper', yref = 'paper',
                  x = 0.05, y = 0.95,
                  text = paste('Source:Data from www.ncdc.noaa.gov\n Visualization: JuanmaMN (Twitter @Juanma_MN)'),
                  font = list(family = 'Arial', size = 8, color = 'rgb(150,150,150)'),
                  showarrow = FALSE) 

```




<br>




**Code, questions and feedback**

The code for this article is published in my [github account](https://github.com/JuanmaMN/plotly).  


Please feel free to follow me on my [Twitter account](https://twitter.com/Juanma_MN) and ask any question or feedback you might have.

Thank you very much for your time  in reading the article.