---
title: "Global Land and Ocean Temperature Anomalies"
author: "JuanmaMN"
date: "6 April 2019"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(ggplot2)
library(plotly)

library(readxl)
Temperature <- read_excel("Temperature.xlsx")
View(Temperature)


Temperature$colour <- ifelse(Temperature$Value < 0, "firebrick1","steelblue")

Temperature_2<-select(Temperature,1:2)
```

## Global Land and Ocean Temperature Anomaly data - Time Series 


[The National Oceanic and Atmospheric Administration](https://www.noaa.gov/) has published the time series of temperature anomalies.

Average temperature data shows a rise in global average temperature over the past several decades year. 

- [Data source](https://www.ncdc.noaa.gov/cag/global/time-series)

- [For more information](https://www.ncdc.noaa.gov/cag/global/data-info)

Please find the analysis using both plotly and ggplot as a project.

### Plotly

```{r plot, echo=FALSE, warning = FALSE}


 plot_ly(Temperature, x=~Year, y=~Value, mode="markers", type="bar", color=~colour , text = ~paste('Year: ', Year, '</br> Value(°C): ', Value)) %>% 
   layout(title = "Global Land and Ocean Temperature Anomalies",xaxis = list(title = ""), yaxis = list(title = "anomaly(°C)"),
          annotations = 
            list(text = "Data from www.ncdc.noaa.gov ", 
                 showarrow = F, xref='paper', yref='paper', 
                 xref = 'paper', x = 0,
                 yref = 'paper', y = 1,
                 font=list(size=10, color="black"))
   )  %>% hide_legend()

```


### Plotly with slider

```{r pressure, echo=FALSE, warning = FALSE}


 plot_ly(Temperature, x=~Year, y=~Value, mode="markers", type="bar", color=~colour , text = ~paste('Year: ', Year, '</br> Value(°C): ', Value)) %>% 
   layout(title = "Global Land and Ocean Temperature Anomalies",xaxis = list(title = ""), yaxis = list(title = "anomaly(°C)"),
          annotations = 
            list(text = "Data from www.ncdc.noaa.gov ", 
                 showarrow = F, xref='paper', yref='paper', 
                 xref = 'paper', x = 0,
                 yref = 'paper', y = 1,
                 font=list(size=10, color="black"))
   )  %>% hide_legend()%>%rangeslider(Temperature$Year[1880],Temperature$Year[2019])

```


### Gplot

```{r, echo = FALSE}



g<- ggplot(Temperature,aes(x=Year, y=Value))+
  geom_bar(stat="identity",position="identity",aes(fill = colour), show.legend = FALSE) + 
  labs(title = "Global Time Series", subtitle = "Global Land and Ocean Temperature Anomalies", caption = "based on data from www.ncdc.noaa.gov") + ylab("anomaly(°C)")+xlab("")

g


```

## Code, questions and feedback

The code for this article is publish in my [github account](https://github.com/JuanmaMN).

Please feel free to reach out for any question or feedback.