---
title: "Health & Education Expenditure by country"
author: "Juanma Martinez"
date: "15/05/2019"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(scales)
library(plotly)
data_plotly_Education_Health <- read_csv("data_plotly_Education_Health.csv")
View(data_plotly_Education_Health)
```



The following graph analyzes % of GDP spend on Health and Education by country.

**Data source used**

This analysis contains data from [World Bank](https://data.worldbank.org/).

The two variables analyzed are the following ones:

- [Current health expenditure (% of GDP)](https://data.worldbank.org/indicator/SH.XPD.CHEX.GD.ZS)

- [Government expenditure on education, total (% of government expenditure)](https://data.worldbank.org/indicator/SE.XPD.TOTL.GD.ZS)

```{r cars,echo=FALSE, warning=FALSE}
p_Education_Health <-   plot_ly(data_plotly_Education_Health, 
                      x = ~Education_expenditure, 
                      y = ~Health_expenditure, 
                      color = ~Continent, 
                      frame = ~Year, 
                      size = ~Population,
                      text =  ~paste('</br> Country: ', Country,
                                     '</br> Year: ', Year,
                                     '</br> Population: ', comma_format()(Population),
                                     '</br> Government expenditure on education (% of GDP): ', Education_expenditure,
                                     '</br> Current health expenditure (% of GDP): ', Health_expenditure), 
                      
                      
                      hoverinfo = "text",
                      type = 'scatter',
                      mode = 'markers'
) %>%
  animation_slider(
    currentvalue = list(prefix = "Year ", font = list(color="red"))
  ) %>%
  
  layout(xaxis = list(range = c(0, 15), title = 'Government expenditure on education (% of GDP)'),
         yaxis = list(range = c(0,20), title = 'Current health expenditure (% of GDP)'),
         title = 'Health & Education Expenditure by country',
         annotations = 
           list(text = "Data from data.worldbank.org", 
                showarrow = F, xref='paper', yref='paper', 
                xref = 'paper', x = 1,
                yref = 'paper', y = 0,
                font=list(size=12, color="black")))


p_Education_Health
```

## R Packages used

This is is an R Markdown document, written in [R Markdown](http://rmarkdown.rstudio.com), with **R** code chunks that use the following packages: 


- [readr](https://cran.r-project.org/web/packages/readr/index.html)
- [dplyr](https://dplyr.tidyverse.org/)
- [tidyr](https://blog.rstudio.com/2014/07/22/introducing-tidyr/)
- [plotly](https://plot.ly/r/)



## Code, questions and feedback

The code for this article is published in my [github account](https://github.com/JuanmaMN/plotly).  

The article has been published on my [website](https://juanmaintro.netlify.com/2019/05/15/health-education-expenditure-by-country-2000-2016/)


Please feel free to reach out for any question or feedback.
