---
title: "Environment - CO2 emissions (kt)  by decade"
author: "Juanma Martinez"
date: "10/05/2019"
output: html_document
---



```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
CO_emissions_3 <- read_excel("CO_emissions_3.xlsx", 
                             col_types = c("text", "text", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric"))
View(CO_emissions_3)

library(tidyr)
library(dplyr)
library(plotly)


CO_emissions_4<-CO_emissions_3 %>%
  gather(Year,C02emissions, `1960`:`2014`)%>%
  select(3,4)%>% 
  group_by(Year) %>%
  summarize(total_emissions=sum(C02emissions, na.rm=TRUE))



CO_emissions_5<-CO_emissions_4%>%
  mutate(
    decade=case_when(
    CO_emissions_4$Year %in% 1960:1969 ~ "1960-1969",
    CO_emissions_4$Year %in% 1970:1979 ~ "1970-1979",
    CO_emissions_4$Year %in% 1980:1989 ~ "1980-1989",
    CO_emissions_4$Year %in% 1990:1999 ~ "1990-1999",
    CO_emissions_4$Year %in% 2000:2009 ~ "2000-2009",
    CO_emissions_4$Year %in% 2010:2014 ~ "2010-2014",
    TRUE ~ as.character(CO_emissions_4$Year)
  )
  ) %>% select(3,2) %>% group_by(decade)%>%
  summarize(total_emissions=sum(total_emissions, na.rm=TRUE))

  
View(CO_emissions_5)

```



The following graph analyzes the Carbon dioxide emissions trend by decade. Emissions continue to increase decade by decade significantly since the study starts according to  [World Bank data](data.worldbank.org)



```{r cars, echo=FALSE, warning=FALSE}

t <- list(
  family = "sans serif",
  size = 16,
  color = 'black')

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)



p <- plot_ly(CO_emissions_5,
  y = ~total_emissions,
  x = ~decade,
  type = "bar",
  text =  ~paste('</br> Decade: ', decade,
                 '</br> Total emissions: ', round(total_emissions,2)),
  
    hoverinfo = "text",
  marker = list(color = 'rgb(158,202,225)',
                line = list(color = 'rgb(8,48,107)', width = 1.5))) %>%
  layout(title = "Co2 emissions by decade", font=t, autosize = F, width = 800, height = 500, margin = m)%>%
  layout(
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         annotations = 
           list(text = "Data from data.worldbank.org", 
                showarrow = F, xref='paper', yref='paper', 
                xref = 'paper', x = 0,
                yref = 'paper', y = 1,
                font=list(size=8, color="black"))) %>%
  add_annotations(
  x= 5,
  y= 170000000,
  xref = "2010-2014",
  yref = "170M",
  text = "Five years of data",
  showarrow = T
)


p

```



```{r}

```



```{r}

```



## R Packages used

This is is an R Markdown document, written in [R Markdown](http://rmarkdown.rstudio.com), with **R** code chunks that use the following packages: 


- [readxl](https://readxl.tidyverse.org/)
- [dplyr](https://dplyr.tidyverse.org/)
- [tidyr](https://blog.rstudio.com/2014/07/22/introducing-tidyr/)
- [plotly](https://plot.ly/r/)



## Code, questions and feedback

The code for this article is published in my [github account](https://github.com/JuanmaMN/plotly).   [For Website link](https://juanmaintro.netlify.com/2019/05/10/co2-emissions-kt-by-decade/)


Please feel free to reach out for any question or feedback.
